\chapter{Introduction} \label{chp:introduction}

\section{Thesis Statement}

With this research into filesystem, device driver, and hardware Flash
Translation Layer (FTL) based Full Disk Encryption (FDE) schemes for ``data at
rest'', we primarily consider: (1) the established wisdom in the crypto
community that stream ciphers are unsuitable for FDE and (2) exploring the
tradeoff space made between total energy use, filesystem performance, and
reasonable security guarantees when comparing specific cipher configurations. In
the first case, we develop and implement a secure approach to FDE based on
stream ciphers, the proliferation of secure hardware, and the characteristics of
Log-Structured Filesystems (LFS). In the second case, we implement a dozen
stream ciphers---each exposing several knobs---and demonstrate navigating our
tradeoff space via runtime cipher switching while maintaining reasonable
security guarantees. We then present a formal analysis of our system's security
guarantees. Finally, we consider data authenticity schemes using some of the
same cryptographic primitives but in the context of ``data in motion'' through
the development and implementation of a resource verification protocol expanding
on de facto checksum-based integrity protections to defeat co-hosting while
automating the tedious parts of checksum verification.

\section{Contributions}

\subsection{StrongBox}

StrongBox is a novel scheme for securing data at rest and is a drop-in
replacement for AES-XTS-backed FDE such as dm-crypt~\cite{dmcrypt}. StrongBox
uses a fast stream cipher for confidentiality and performance with integrity
preserving Message Authentication Codes~\cite{MAC} and a secure, persistent
hardware counter to ensure integrity and counter the weaknesses inherent in
stream cipher based FDE. With StrongBox's, we present a system design enabling
the first confidential, high-performance drive encryption scheme based on stream
ciphers.

\subsection{SwitchCrypt}

SwitchCrypt is software mechanism that navigates the tradeoff space made by
balancing competing security and latency requirements via \emph{cipher
switching} in space or time and represents a vastly improved FDE approach based
on StrongBox. SwitchCrypt addresses the reality that optimizing for performance
often conflicts with other key concerns like energy usage and desired security
properties. SwitchCrypt leverages the behavior of underlying solid-state storage
to trade between throughput, energy use, and desirable security properties of
various ciphers. This is accomplished dynamically and at run time.

\subsection{HASCHK}

HASCHK is a resource verification protocol expanding on de facto checksum-based
integrity protections to defeat co-hosting while automating the tedious parts of
checksum verification. HASCHK mitigates the authenticity risks of data in
motion; in this instance: downloading resources over the internet. We find our
approach is more effective than existing mitigation methods, significantly
raises the bar for the attacker, and is deployable at scale.
