\chapter{Conclusion} \label{chp:conclusion}

The conventional wisdom is that securing data at rest requires one must pay the
high performance overhead of encryption with AES is XTS mode. This work shows
that technological trends overturn this conventional wisdom: log-structured file
systems and hardware support for secure counters make it practical to use a
stream cipher to secure data at rest. We demonstrate this practicality through
our implementation of StrongBox which uses the ChaCha20 stream cipher and the
Poly1305 MAC to provide secure storage and can be used as a drop-in replacement
for dm-crypt.

Our empirical results show that under F2FS---a modern, industrial-strength
Log-structured file system---StrongBox provides upwards of $2\times$ improvement
on read performance and average $1.27\times$ improvement on write performance
compared to dm-crypt. Further, our results show that F2FS plus StrongBox
provides a higher performance replacement for Ext4 backed with dm-crypt. We make
our implementation of StrongBox available open source so that others can extend
it or compare to it.\footnote{\StrongBoxURI} Our hope is that this work
motivates further exploration of fast stream ciphers as replacements for AES-XTS
for securing data at rest.

Further, this work advocates for a more flexible approach to FDE where the
storage system can dynamically adjust the tradeoffs between security and
latency/energy. To support this vision of agile encryption, we proposed an
interface that allows multiple stream ciphers with different input and output
characteristics to be composed in a generic manner. We have identified three
strategies for using this interface to switch ciphers dynamically and with low
overhead. We have also proposed a quantification framework for determining when
to use one cipher over another. Our case studies show how different strategies
can be used to optimize for different goals in practice. We believe that agile
encryption will become increasingly important as successful systems are
increasingly required to balance conflicting operational requirements. We hope
that this work inspires further research in achieving this balance. Our work is
publicly available open-source\footnoteref{note1}.

When it comes to data in motion---specifically, downloading arbitrary resources
over the internet---it is indeed a risky endeavor. Resource integrity and other
Supply Chain Attacks are becoming more frequent and their impact more widely
felt. In this work, we showed that the de facto standard for protecting the
integrity of arbitrary resources on the internet---the use of
\emph{checksums}---is insufficient and often ineffective. We presented HASCHK, a
practical resource verification protocol that automates the tedious parts of
checksum verification while leveraging pre-existing high availability systems to
ensure resources and their checksums are not vulnerable to co-hosting. Further,
we demonstrated the effectiveness and practicality of our approach versus
real-world resource integrity attacks in a production application.

The results of our final evaluation show that our approach is more effective
than checksums and prior work mitigating integrity attacks for arbitrary
resources on the internet. Further, we show HASCHK is capable of guarding
against a variety of attacks, is deployable at scale for providers that already
maintain a DNS presence, and can be deployed without fear of adversely affecting
the user experience of clients that are not HASCHK-aware. Though not a panacea,
we believe our protocol significantly raises the bar for the attacker. We intend
to continue developing our extension and we make it available to a wide audience
(see \cref{app:availability}).

\section{Future Work}

As it stands now, our StrongBox and SwitchCrypt implementations are single
threaded. The cryptographic systems we compared to StrongBox and SwitchCrypt and
all multi-threaded, perhaps making our performance wins more significant. What
performance gains (i.e. more slack) might be available if we parallelize
portions of StrongBox and SwitchCrypt source? Examples include: 1) given that
nuggets are all independent agents, new switching strategies might be developed
that leverage any speedups in parallelizing the encryption and decryption
processes and 2) garbage collection and cipher switching can happen in
background worker threads and could even leverage a scheduler and 3) StrongBox
and SwitchCrypt could be integrated into F2FS directly, sharing its
threading/scheduling model in a production implementation; currently, StrongBox
and SwitchCrypt are implemented on top of the BUSE emulation device.
