\acknowledgments
I would first and foremost like to thank my advisor, Dr. Henry (Hank) Hoffmann.
Without your compassion, patience, conscientiousness, and cosmic wealth of
knowledge and experience, none of this work would have been possible. Thank you
for everything you've done for my students and me. You are truly a rare ally.

I'd like to thank my committee members Dr. Ariel J. Feldman (Applied Crypto),
Dr. Haryadi S. Gunawi (Filesystems), and Dr. David Cash (Theoretical Crypto) for
all their hours of hard work and tireless dedication even in the middle of a
pandemic. I learned so much studying under you. Hopefully I spelled everyone's
names correctly this time, haha!

I'd also like to acknowledge my former students Richard Anthony Alvarez and
Trevor James Medina for their huge contributions to HASCHK and to my sanity. Of
course there's Abe (a fullstack flexer!), Mark (remember the name, it'll be on a
ballot some day), Malik, Michael, Tyrese, Ephriam, Matthew, Rakim, Malcolm,
Byron, Leroy, and all my former BDPA kids... I love you guys.

I'd be remiss if I did not acknowledge the pivotal role played by my lovely
hyper-intelligent mother (I had to get it from somewhere) Michelle Davis who,
throughout my childhood, \emph{always} had money for Computer Science workbooks
(but somehow not McDonalds!); as well as my father Bernard Dickens II for always
taking the extra effort to be there for me and always with my best interests at
heart. Thank yous also go out to: my inspiring siblings Davis and Milan; Zara
for the infinity life lessons---you were my rock, my reality hook; Jeff Holmes
of the old Chicago Broadway Armory for showing an eight-year-old me just how fun
and powerful computers can be; Von Steuben high school Computer Science teachers
Stirling Crow and Andres Hernandez for teaching me web design and gifting me the
wisdom to ``use my powers for good;'' my coach Audra Anderson and the BDPA for
teaching me humility and how to be an effective and engaging teacher; Dr.
Rahmelle Thompson of the Morehouse College Hopps Scholars program for revealing
my trajectory to me; Dr. Adrienne Raglin of the Department of Defense Army
Research Laboratory for putting up with me (twice!) and teaching me what real
research looks like; neighborhood matriarch Martha Alvarez for looking out for
me during my last few years in Chicago; the University of Chicago and all its
faculty and staff for fostering a culture of socially conscious elite
intellectual pursuit; President Barack H. Obama and Senator Elizabeth Warren for
demonstrating black excellence and how to persist nevertheless; and all my
mentors, former students, and true friends over the years for their unwavering
support throughout this process. Know I would not have made it without every
last one of you.

I must give special thanks to my UChicago family: Connor. Our interactions were
usually brief, but you blazed the trail for me in particular... I was so nervous
(my default state!) but hearing you talk about your experiences
post-M.S.-defense really helped me calm down and focus. Thank you and Saeid for
all your wisdom. Anne, thanks for listening to my boring talk! Your feedback
during the group meeting really helped hone my presentation. Ivanna and Will,
thank you for reaching out! I'm just a hopeless recluse. Kavon, our
conversations were fun. Huazhe would greet me on those rare occasions I entered
the office... thank you for the warm welcomes! Nikita, Yi, Santriaji, Yuli,
Tejas, Ahsan, it was my pleasure to get to know you all.

This material is based upon work supported by the National Science Foundation
under Grant No. CNS-1526304. So thank you too United States discretionary
spending budget authorized by Congress.
