\section{Motivation} \label{sec:sc-motivation}

The state of the art for securing data at rest, such as the contents of a
laptop's SSD, is Full Drive Encryption (FDE). Traditional FDE employs a single
cryptographic cipher to encrypt, decrypt, and authenticate drive contents on the
fly. Unfortunately, encryption introduces overhead that drastically impacts
system performance and total energy consumption. Hence, modern storage systems
must carefully balance these competing concerns. On the one hand, stronger
security guarantees come with increased latency and threaten to balloon energy
consumption. On the other, capping total energy consumption requires tolerating
increased latency or weaker security guarantees.

FDE implementations such as dm-crypt~\cite{dmcrypt,DmC-Android} for Linux and
BitLocker for Windows balance these concerns with respect to some generic
``common case'' workload, but this approach often fails to deliver an optimal
outcome for specific workloads. Google's Android OS is a good example. Android
supported FDE with the release of Android 3.0, yet it was not enabled by default
until Android 6.0~\cite{android-M-mobile-motivation}. Two years prior, Google
attempted to roll out FDE by default on Android 5.0 but had to backtrack. In a
statement to Engadget, Google blamed ``'performance issues on some partner
devices' ... for the backtracking''~\cite{google-engadget}. At the same time,
AnandTech reported a ``62.9\% drop in random read performance, a 50.5\% drop in
random write performance, and a staggering 80.7\% drop in sequential read
performance'' versus Android 5.0 unencrypted storage for various
workloads~\cite{android-M-mobile-motivation-2}.

FDE's impact on drive performance and energy efficiency depends on a multitude
of choices. Paramount among them is the choice of cipher, as different ciphers
expose different performance and energy efficiency characteristics. In this way,
cipher choice can be viewed as a key \emph{configuration parameter} for FDE
systems. The benefits of choosing one cipher over another might include: 1)
improved performance (\ie{overall reduction in FDE overhead}), 2) reduced energy
use, 3) more useful security guarantees, and 4) the ability to encrypt devices
that would otherwise be too slow or energy-inefficient to support FDE.

However, the standard cipher choice for FDE is the slow AES \emph{block cipher}
(AES-XTS)~\cite{XTS, XTSComments, NISTXTS}. With StrongBox, we introduced a
method for using ciphers other than AES-XTS for FDE; specifically, the high
performance ChaCha20 \emph{stream cipher}~\cite{StrongBox, ChaCha20}. More
recent work---such as Google's HBSH (hash, block cipher, stream cipher, hash)
and Adiantum~\cite{Adiantum}---brings stream cipher based FDE to devices that do
not or cannot support hardware accelerated AES. Hence, it has been demonstrated
that using stream ciphers for FDE is both desirable in a variety of contexts and
feasible at industry scale.

With this research, we explore the rich configuration space of stream ciphers
beyond the narrow scope of previous work. Each cipher comes with a variety of
performance, energy efficiency, and security properties in the FDE context.
These ciphers include ChaCha variants with different round counts (e.g.,
ChaCha8 and ChaCha12)~\cite{ChaCha20}, ciphers with stronger security
guarantees versus more robust adversaries (e.g., Freestyle~\cite{Freestyle}),
and other ciphers like SalsaX~\cite{SalsaX}, AES in counter mode
(AES-CTR)~\cite{AESCTR}, Rabbit~\cite{Rabbit}, Sosemanuk~\cite{Sosemanuk}, etc.
Given this variety, the cipher configuration providing the least latency
overhead is almost always different than the configuration providing the most
desirable security properties, and both may differ from the configuration using
the least energy or preserving the most free space on the encrypted drive.

Further, while cipher choice might be configured statically at compile or boot
time with respect to some common case in traditional FDE, such configurations
cannot dynamically adapt to changes that arise while the system is running.
Examples include changes in resource availability, runtime environment, desired
security properties, and respecting changing OS energy budgets.

Hence, any static common-case FDE configuration will sacrifice one concern for
another, even when it is not optimal to do so for a given workload. But what if
a system could dynamically transition into a more desirable configuration given
runtime changes?\\
\\
\textbf{Our Contributions}\\
To realize the goal of dynamically adjusting storage tradeoffs at runtime, we:

\begin{itemize}
  \item Define a scheme to \emph{quantify} the usefulness of each cipher based
  on key security properties relevant to FDE in context. Using this scheme, we
  define a tradeoff space of cipher configurations over competing concerns:
  total energy use, desirable security properties, read and write performance
  (latency), total writable space on the drive, and how quickly the contents of
  the drive can converge to a single encryption configuration.

  \item Introduce a novel design substantively expanding prior FDE work by
  wholly \emph{decoupling} cipher implementations from the encryption process.

  \item Develop the idea of cipher switching using \emph{switching strategies}
  to ``re-cipher'' storage units dynamically, allowing us to tradeoff different
  performance and security properties of various configurations at runtime.
\end{itemize}

Unifying these contributions, we present SwitchCrypt: a software system that
navigates the tradeoff space made by balancing competing security and latency
requirements via cipher switching in space and time. We implement SwitchCrypt
and three switching strategies---\emph{Forward}, \emph{Selective}, and
\emph{Mirrored}---to dynamically transition the system between configurations
using our generic cipher interface. We then study the utility of cipher
switching through three case studies where latency, energy, and desired security
properties change over time.

In one study, where we require the filesystem to react to a shrinking energy
budget by switching ciphers, we find that SwitchCrypt achieves up to a 3.3x
total energy use reduction compared to prior static approaches that only use the
Freestyle stream cipher without switching. In another case, where we allow the
user to manually switch between ChaCha20 and Freestyle stream ciphers
dynamically, we achieve a 3.1x to 4.8x reduction to read latency and 1.6x to
2.8x reduction to write latency compared to prior static approaches.

We make the SwitchCrypt source publicly available open
source\footnote{\label{note1}\SwitchCryptURI}.

\subsection{Example: Filesystem Reacts to ``Battery Saver''}

Suppose we have an ARM-based ultra-low-voltage netbook provided to us by our
employer. As this is an enterprise device, our employer requires that 1) our
drive is fully encrypted at all times and 2) our encrypted data is constantly
backed up to an offsite system. The industry standard in full drive encryption
is AES-XTS, so we initialize our drive with it. Given these requirements, three
primary concerns present themselves.

First, it is well known that FDE using AES-XTS adds significant latency and
power overhead to I/O operations, especially on mobile and battery-constrained
devices~\cite{google-engadget, android-M-mobile-motivation,
android-M-mobile-motivation-2}. To keep our drive encrypted at all times with
AES-XTS means we must accept this hit to performance and battery life. Worse, if
our device does not support hardware accelerated AES, performance can be
degraded even further; I/O latency can be as high as 3--5x~\cite{StrongBox}.
Hardware accelerated AES is hardly ubiquitous, and the existence of myriad
devices that do not support it cannot simply be ignored, hence Google's
investment in Adiantum---an FDE solution for ``the next billion users'' of
low-cost devices without support for hardware accelerated AES~\cite{Adiantum}.

Second, AES-XTS is designed to mitigate threats to drive data ``at rest,'' which
assumes an attacker cannot access snapshots of our encrypted data nor manipulate
our data without those manipulations being immediately obvious to us. With
access to multiple snapshots of a drive's AES-XTS-encrypted contents, an
attacker can passively glean information about the plaintext over time by
contrasting those snapshots, leading to confidentiality violations in some
situations~\cite{XEX, XTS}. Similarly, an attacker that can manipulate encrypted
bits without drawing our attention will corrupt any eventual plaintext,
violating data integrity and, in the worst case, influencing the behavior of
software. Unfortunately, in real life, data rarely remains ``at rest'' in these
ways. In our example, our employer requires we back up the contents of our drive
to some offsite backup service; this service will receive periodic snapshots of
the encrypted state of our drive, violating our ``at rest'' invariant. These
backups occur at a layer above the drive controller, meaning any encryption
happening at the FTL or below is irrelevant.

Third, our system is battery constrained, placing a cap on our energy budget
that can change at any moment as we transition from line power to battery power
and back. Our system should respond to these changing requirements without
violating any other concerns.

To alleviate the performance concern, we can choose a stream cipher like
ChaCha20 rather than the AES-XTS block cipher. Using StrongBox, an encryption
driver built for ChaCha20-based FDE, we can achieve on average a 1.7x speedup
and a commensurate reduction in energy use~\cite{StrongBox}.

When it comes to the security concern, StrongBox solves both the snapshot and
integrity problems by 1) never writing data encrypted with the same key to the
same location and 2) tracking drive state using a Merkle tree and monotonic
counter supported by trusted hardware to prevent rollbacks. This ensures data
manipulations cannot occur and guarantees confidentiality even when snapshots
are compared regardless of the stream cipher used. Unfortunately, restoring from
a backup necessitates a forced rollback of drive state, potentially opening us
back up to confidentiality-violating snapshot comparison
attacks~\cite{StrongBox}.

To truly address the security concern requires a cipher with an additional
security property: \emph{ciphertext randomization}. Without ciphertext
randomization, an attacker can map plaintexts to their ciphertext counterparts
during snapshot comparison, especially if they can predict what might be written
to certain drive regions. However, with ciphertext randomization, a cipher will
output a different ``random'' ciphertext even when given the same key, nonce,
and plaintext; this means, even after a forced rollback of system state and/or
legitimate restoration from a backup, comparing future writes is no longer
violates confidentiality because each snapshot will always consist of different
ciphertext regardless of the plaintext being encrypted or the state of the
drive. Using Freestyle~\cite{Freestyle}, a ChaCha20-based stream cipher that
supports ciphertext randomization, we can guarantee data confidentiality in this
way. So, we switch from StrongBox to an encryption driver that supports
Freestyle.

Unfortunately, like AES-XTS, Freestyle has significant overhead compared to the
original ChaCha20. In exchange for stronger security properties, Freestyle is up
to 1.6x slower than ChaCha20, uses more energy, has a higher initialization
cost, and expands the ciphertext which reduces total writeable drive
space~\cite{Freestyle}.

Further complicating matters is our final concern: a constrained energy budget.
Our example system is battery constrained. Even if we accepted trading off
performance, drive space, and energy for security in some situations, in other
situations we might prioritize reducing total energy use. For example, when we
trigger ``battery saver'' mode, we expect our device to conserve as much energy
as possible. It would be ideal if our device could pause backups and the
encryption driver could switch from the ciphertext-randomizing Freestyle
configuration back to our high performance energy-efficient ChaCha20
configuration when conserving energy is a top priority, and then switch back to
the Freestyle configuration when we connect to a charger and backups are
eventually resumed.

In this dissertation we present SwitchCrypt, a device mapper that can trade off
between these two configurations and others without compromising security or
performance or requiring the device be restarted. With prior work, the user must
select a static operating point in the energy-security-latency space at
initialization time and hope it is optimal across all workloads and cases. If
they choose the Freestyle configuration, their device will be slower and battery
hungry even when they are not backing up. If they choose the more performant
ChaCha20 configuration, they risk confidentiality-violating snapshot comparison
attacks. SwitchCrypt solves this problem by encrypting data with the high
performance ChaCha20 when the battery is low and switching to Freestyle when
plugged in and syncing with the backup service resumes.

\subsection{Key Challenges}

To trade off between different cipher configurations, we must address three key
challenges. First, we must determine what cipher configurations are most
desirable in which contexts and why. This requires we \emph{quantify} the
desirable properties of these configurations. Second, we must have some way to
encrypt independent storage units with any one of these configurations. This
requires we \emph{decouple} cipher implementations from the encryption process
used in prior work. Third, we need to determine when to re-encrypt those units,
which configuration to use, and where to store the output, all with minimal
overhead. This requires we implement efficient cipher \emph{switching
strategies}.

\textbf{Quantifying the properties traded off between configurations.} To obtain
a space of configurations that we might reason about, it is necessary to compare
certain properties of stream ciphers useful in the FDE context. However,
different ciphers have a wide range of security properties, performance
profiles, and output characteristics, including those that randomize their
outputs and those with non-length-preserving outputs---\ie{the cipher outputs
more data than it takes in}. To address this, we propose a framework for
quantitative cipher comparison in the FDE context; we use this framework to
define our configurations.

\textbf{Decoupling ciphers from the encryption process.} To flexibly switch
between configurations in SwitchCrypt requires a generic cipher interface. This
is challenging given the variety of inputs required by various stream ciphers,
the existence of non-length-preserving ciphers, and other differences. We
achieve the required generality by defining independent storage units called
\emph{nuggets}; we borrow this terminology from prior work (see
\cite{StrongBox}) to easily differentiate our logical blocks (nuggets) from
physical drive and other storage blocks. And since they are independent, we can
use our interface to select any configuration to encrypt or decrypt any nugget
at any point.

\textbf{Implementing efficient switching strategies.} Finally, to determine when
to switch a nugget's cipher and to where we commit the output, we implement a
series of high-level policies we call \textit{cipher switching strategies}.
These strategies leverage our generic cipher interface and flexible drive layout
to selectively ``re-cipher'' groups of nuggets, whereby the key and the cipher
used to encrypt/decrypt a nugget are switched at runtime. These strategies allow
SwitchCrypt to move from one configuration point to another or even settle on
optimal configurations wholly unachievable with prior work. The challenge here
is to accomplish this while minimizing overhead.
